Master's Project Journal

### 2019-03-14 tex_files/Journal.tex
journal

\section*{Ring Osc Locking}
After many trials and tribulations, including a situation where the ring adpll was locking to the inverse of the reference applied to it I finally managed to get the ring locked at 5 MHz with a 4 times divider. Turns out the shifting of $K_p$ and $K_i$ in the same direction did not help matters as I thought it might.
In fact increasing $K_p$ while decreasing $k_i$ turned out to be the solution to my problems.
Along the way I located an error where I was using 5'd16 as the bias which doesnt work with a subtraction of 15 to -16, as it would give overflow. Athough I had actually  made the counter the same in both directions so this didnt actually manifest itself as an issue.
The lock range is now heavily impacted by the gains as I discovered when attempting to copy gains from the PA ADPLL.
The key to solving it was going through all the fixed point arith. and checking that the widths made sense, which made my realise I had made a false assummtion that going from an 8 to a 5 bit detector/filter resulted in a div by eight times more at the exit of the filter, but in fact had the same div by 4.
After discovering this I had it locking within 3 hours of work, when prior I had spent ~ 9 days on the calendar and ~30 hours working on the problem. Locking perofmance looks potentially better than the 10 MHz perf of the ADPLL (magnitude not \% for the sake of comp. However div is by 4 now not 8, and res is twice as good.) In the coming week I will be characterising the perf of these different designs to compare effectively.

@@

\section*{Twas the week before the midterm}
This week was eventful but frustrating. I did not manage to make progress on any goals per say, but I discovered what was the cause behind the inverse locking that I had been seeing sometimes. Turns out it was being caused by the phase detector design which I was using being stable for very small gains and a small number of bit phase detection and if the falling edge of signal 1 toggled back and forth between rising on signal two I would get oscillation between positive and negative, or lead and lag to use the correct terms, and with the tiny gains making it actually stable in this state. Changing the detector to a more conventional style that did not terminate a measurement until the next rising edge on the opposite signal fixed this probem. The new issue now is that I cannot get low jitter locking, seeingly down to the behaviour of the loop filter.\\
The loop filter appears to work correctly when the two paths are taken in isolation but when combining the paths it breaks down. Either through being too aggressive and doesnt lock or from the ki value being too small, and when it is too small the output of the loop filter toggles between a value of min and maxval thus creating a huge amount of jitter.
\end{document}

>>>>

\section*{Ring Osc Locking}
After many trials and tribulations, including a situation where the ring adpll was locking to the inverse of the reference applied to it I finally managed to get the ring locked at 5 MHz with a 4 times divider. Turns out the shifting of $K_p$ and $K_i$ in the same direction did not help matters as I thought it might.
In fact increasing $K_p$ while decreasing $k_i$ turned out to be the solution to my problems.
Along the way I located an error where I was using 5'd16 as the bias which doesnt work with a subtraction of 15 to -16, as it would give overflow. Although I had actually  made the counter the same in both directions so this didnt actually manifest itself as an issue.
The lock range is now heavily impacted by the gains as I discovered when attempting to copy gains from the PA ADPLL.
The key to solving it was going through all the fixed point arith. and checking that the widths made sense, which made my realise I had made a false assummtion that going from an 8 to a 5 bit detector/filter resulted in a div by eight times more at the exit of the filter, but in fact had the same div by 4.
After discovering this I had it locking within 3 hours of work, when prior I had spent ~ 9 days on the calendar and ~30 hours working on the problem. Locking perofmance looks potentially better than the 10 MHz perf of the ADPLL (magnitude not \% for the sake of comp. However div is by 4 now not 8, and res is twice as good.) In the coming week I will be characterising the perf of these different designs to compare effectively.

@@

\section*{Twas the week before the midterm}
This week was eventful but frustrating. I did not manage to make progress on any goals per say, but I discovered what was the cause behind the inverse locking that I had been seeing sometimes. Turns out it was being caused by the phase detector design which I was using being stable for very small gains and a small number of bit phase detection and if the falling edge of signal 1 toggled back and forth between rising on signal two I would get oscillation between positive and negative, or lead and lag to use the correct terms, and with the tiny gains making it actually stable in this state. Changing the detector to a more conventional style that did not terminate a measurement until the next rising edge on the opposite signal fixed this probem. The new issue now is that I cannot get low jitter locking, seeingly down to the behaviour of the loop filter.\\
The loop filter appears to work correctly when the two paths are taken in isolation but when combining the paths it breaks down. Either through being too aggressive and doesnt lock or from the ki value being too small, and when it is too small the output of the loop filter toggles between a value of min and maxval thus creating a huge amount of jitter.
\section{pm 10 nano}
I finally have got good performance but I am not sure if I solved the problem. Four main changes were made, which in isolation had little impact. Firstly in order to obtain a full output range I removed the extra bits being added in the loop filter after multiplied by ki or kp. This meant that a division by four of a number where the upper bit was empty became a div two with the whole number thus doubling the output range. The second change was to move the cycle delay from the input to output of the loop filter thus ensuring that the output would change at a more appropriate time. I also chose to clock this on a signal from earlier in the inverter chain thus ensuring it would always be finished changing before the clock edge. I also swapped the size of the control code and detector width to match the design of the PA, so I went from 5 bit cc and 6 bit error to 6 bit cc and 5 bit error.

As a result of these changes I was able to get a scope image where there was plus minus 10 nanoseconds on the edge visible in screen. Down from 40 nanoseconds that I had had on Tuesday AM and down from the 40\% ish of the period with the divider in place. I did remove the divider for this testing to make things easier and as of Thursday 14/03 it had not been replaced. The plan is that next week I will reimplement the divider and once I have better aligned the 4 PLLs I have, go up to a 3x3 network.

\end{document}
